### 2017-01-17 thesis/latex/thesis.tex
Add finishing touches on tests section of Methods.

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{array}

@@

\listoffigures
\newpage

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.85\textwidth,keepaspectratio]{../figures/mechanochemical-cycle.jpeg}
  \caption{Cycle of states the dynein motor goes through during motion in the Cianfrocco model \cite{cianfroccoreview}.}
  \label{mech-cycle}
\end{figure}

@@

This test verifies both force and velocity are calculated properly for either model. If either force or velocity was wrong, then the model would not obey the Boltzmann hypothesis $P(s) = e^{-\Delta G_{s}/K_BT}$, where $s$ is a state of the system. The transition rate from $s_1$ to $s_2$ is $P(s_1\rightarrow s_2) = e^{-{\Delta G_2 - \Delta G_1}/K_BT}$. Wrong velocities are those that do not transition the system from $s_1$ to $s_2$ at this rate.\\

@@

\begin{figure}[h!]
  \centering
  \begin{minipage}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/OB_Average_PE.pdf}
    \caption{Onebound PE vs time.}
  \end{minipage}
  \begin{minipage}[b]{0.49\textwidth}
    \includegraphics[width=\textwidth]{../figures/BB_Average_PE.pdf}
    \caption{Bothbound PE vs time.}
  \end{minipage}
  \label{equipartition_agreement}
\end{figure}

@@

\section{Questions for David}
\begin{itemize}
\item Would it be possible to, for the ET test, also verify the standard deviation of energy is what it should be? Since just verifying the energy averages to N/2KbT doesn't verify the forces are correct, but the stdev would?
\end{itemize}

\section{Figures to make}
\begin{itemize}
\item Crystal structure of dynein with rigid rods imposed and or a cartoon model
\item Brownian motion figure
\item Crystal structure transitioning from pre/post stroke
\item dt vs error plot
\item ET angle histogram
\item figure of finding lengths in PyMol
\item stepping length/time histograms
\end{itemize}
\end{document}

>>>>

@@

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=.65\textwidth,keepaspectratio]{../figures/mechanochemical-cycle.jpeg}
  \caption{Cycle of states the dynein motor goes through during motion in the Cianfrocco model \cite{cianfroccoreview}.}
  \label{mech-cycle}
\end{figure}

@@

This test verifies both force and velocity are calculated properly for either model. If either force or velocity was wrong, then the model would not obey the Boltzmann hypothesis $P(s) = e^{-\Delta G_{s}/K_BT}$, where $s$ is a state of the system. The transition rate from $s_1$ to $s_2$ is $P(s_1\rightarrow_s_2) = e^{-{\Delta G_2 - \Delta G_1}/K_BT}$. Wrong velocities are those that do not transition the system from $s_1$ to $s_2$ at this rate.\\

@@

%% \begin{figure}[h!]
%%   \centering
%%   \begin{minipage}[b]{0.49\textwidth}
%%     \includegraphics[width=\textwidth]{../figures/OB_Average_PE.pdf}
%%     \caption{Onebound PE vs time.}
%%   \end{minipage}
%%   \begin{minipage}[b]{0.49\textwidth}
%%     \includegraphics[width=\textwidth]{../figures/BB_Average_PE.pdf}
%%     \caption{Bothbound PE vs time.}
%%   \end{minipage}
%%   \label{equipartition_agreement}
%% \end{figure}

@@

\section{Questions for David}
\begin{itemize}
\item Would it be possible to, for the ET test, also verify the standard deviation of energy is what it should be? Since just verifying the energy averages to N/2KbT doesn't verify the forces are correct, but the stdev would?
\end{itemize}
\end{document}
